\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

Huge amount of parallel recordings from hundreds of neurons,
available today, is accompanied by the statistical challenges
to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by
constructing a full description of the 
neuronal firing patterns. The \me\ method employs only first and second
order statistics of the representative random sample to construct 
a \enquote{maximally noncommittal} \cite{jaynes1963} 
probability distribution of the firing patterns [\cite].

>>>>

Huge amounts of parallel recordings from hundreds of neurons,
available today, are accompanied by the statistical challenges
to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by
constructing a full description of the 
neuronal firing patterns. The \me\ method employs only first and second
order statistics of the representative random sample to construct 
a \enquote{maximally noncommittal} \cite{jaynes1963} 
probability distribution of the firing patterns [\cite].
